\textbf{Perius: A Security Management Layer with Copy-on-Write for CDN Assets}

### 2016-03-23 tex/paper.tex
Updated the introduction

%}}}
\title{\textbf{Designing a Security Management Layer with Copy-on-Write for CDN Assets}}
\author{Klingsbo, Lukas}

@@

%}}}
\section{Introduction}
Developing large projects containing static content usually involves using a Content Distribution
Network to be able to scale to a larger user base. The commercial Content Distribution Networks are
usually fairly easy to use, the content that is to be used in a project is usually simply uploaded
and then distributed over the globe when the public requests it. For secret content this can be a
problem and an inconvenience, and that is what this thesis is about. This work examines a way of
enforcing virtual access control on content and groups of content, in the form of containers and
snapshots. A system was developed using the Copy-on-Write principle to improve scalability and make
it a lighter operation to take snapshots.

@@

\subsubsection{Persistent storage} \label{sec:persistent_storage}
\newpage
\subsection{Load Testing} \label{sec:load_testing}
Wrk was used to load test the back-end. It is a multi-threaded benchmarking tool for HTTP which can
create large loads. The testing was done locally on a virtual server having 6 CPU cores and 48GB of
RAM. The results that will be analysed are throughputs performed without breaking the set timeout 
of the server, as that will give a fair judgement of how well the system can perform.

\subsubsection{GET requests} \label{sec:GET_REQUESTS}
To be able to determine what the bottleneck of the back-end is, three different types of \textit{GET
requests} are performed. The first one tries to maximise the number of requests that spray-can (HTTP
server) can handle with the given specifications and therefore the server just returns 200 (OK). The
second request requests the simplest API call which involves getting all currently stored projects
from the MongoDB instance. As this involves the server answering with some payload, the third
request is simply the same amount of static payload as the second request but without involving any
connections to MongoDB. Most responses are JSON structures, except for the ones in
Listing~\ref{OKREQUEST} and Listing~\ref{STATICREQUEST}.\\

\par
The typical requests performed with Wrk in this work will look similar to this:
\begin{lstlisting}[frame=single]
wrk -t100 -c100 -d10s http://perius:8000/ok
\end{lstlisting}
where -t100 means that it uses 100 threads, -c100 that it emulates 100 clients requesting over and
over and -d100s is the amount of time that the load test will run, in this case 100 seconds.

@@

@@

Response data:
[{
  "id": "565cdae1898b798008105fd47",
  "name": Test Project,
  "readOnly": false,
  "lastModified": 1456320024643
}]
\end{lstlisting}
\end{minipage}

\begin{minipage}{\linewidth-1cm}
\begin{lstlisting}[label=STATICREQUEST,caption=Result of static text requests]
wrk -t100 -c100 -d10s http://perius:8000/static

@@

Response data:
Static test data for WRK not involving MongoDB 
or filesystem access. 
Lorem ipsum dolor sit amet.
\end{lstlisting}
\end{minipage}
\end{custommargins}

Listing~\ref{OKREQUEST} shows that the HTTP server can answer about 100K requests/s when not
involving any payload other than status code 200 (OK). When comparing that to the request which
involved the server responding with a small (100 Byte) payload (Listing~\ref{STATICREQUEST}) one can
see that it is about 10\% slower to send some more data, \textasciitilde90K requests/s. However when
comparing that to the requests that needed database access it is obvious that the HTTP server can
handle all the load that it needs to, as Listing~\ref{DBREQUEST} shows that to fetch all documents
in a collection (in this case only one) is dramatically slower, the throughput was only
\textasciitilde7000 requests/s.

@@

The result in Listing~\ref{TREEREQUEST} shows an average of 40 requests/s, which means this is the
real bottleneck in the application. There are two solutions to fix this bottleneck, as the project
tree will not be modified nearly as often as it is requested the first solution would be to cache the
results of the tree requests and invalidate those caches when the tree is modified. The second
solution would be to make a more computationally feasible way of building and fetching the whole 
tree from the database. This is left to implement if the need comes for it in the future. Even
though this massive bottleneck is present, it will not be a problem in a small scale production
environment as the tree is fetched approximately once every 30 seconds by active users, which means
that the application still could support at least 1200 very active users.

@@

>>>>

%}}}
\title{\textbf{Perius: A Security Management Layer with Copy-on-Write for CDN Assets}}
\author{Klingsbo, Lukas}

@@

%}}}
\section{Introduction}
Developing large projects containing static content usually involves using a Content Distribution
Network to be able to scale to a larger user base. The commercial Content Distribution Networks are
usually fairly easy to use. The content that is to be used in a project is uploaded and then
distributed over the globe when a client is trying to access the content. For secret content this
can be a problem and an inconvenience, and that is what this thesis is about.

When looking at the game industry, secret content could be anything from a picture related to a yet
unreleased game to an internal video only intended for employees. Some secret content needs to stay
secret and some content needs to get its security restraints changed during time. For example when a
game is in a closed alpha stage, the content should only be accessible by the people working on it.
But when that game later moves into an open beta phase (open for public), the content needs to be
publicly accessible.

As large projects most often are divided into different dividable parts, a concept called containers
is introduced in this work. Containers can contain more containers and content and when
modifying the security settings for a container it is applied recursively to all its content and
sub-containers.

This work examines a way of enforcing virtual access control on content and groups of content, in
the form of containers and snapshots to be able to handle the secrecy requirements easily. A system
was developed using the Copy-on-Write principle to improve scalability and make it a lighter
operation to take snapshots of parts of the system.

@@

\subsubsection{Persistent storage} \label{sec:persistent_storage}
\newpage
\subsection{Load Testing} \label{sec:load_testing}
Wrk and Apache Bench was used to load test the back-end. Wrk is a multi-threaded benchmarking tool
for HTTP which can create large loads and Apache Bench has similar capabilities, but is better
suited for file uploads than Wrk. The testing was done locally on a virtual server having 6 CPU
cores and 48GB of RAM. The results that will be analysed are the throughput of each request
performed without breaking the set timeout of the server, as that will give a fair judgement of how
well the system can perform.

\subsubsection{GET requests} \label{sec:GET_REQUESTS}
To be able to determine what the bottleneck of the back-end is, three different types of \textit{GET
requests} are performed. Most responses are JSON structures, except for the ones in
Listing~\ref{OKREQUEST} and Listing~\ref{STATICREQUEST}, which can be seen in the Response data part
of the listings.\\

The typical requests performed with Wrk in this work will look similar to this:
\begin{lstlisting}[frame=single]
wrk -t100 -c100 -d10s http://perius:8000/ok
\end{lstlisting}
where -t100 means that it uses 100 threads, -c100 that it emulates 100 clients requesting over and
over and -d100s is the amount of time that the load test will run, in this case 100 seconds.

@@

\par
The first request (Listing~\ref{OKREQUEST}) tries to maximise the number of requests that spray-can
(HTTP server) can handle with the given specifications and therefore the server just returns 200
(OK).

@@

Response data:
[{
  "id": "565cdae1898b798008105fd47",
  "name": Test Project,
  "readOnly": false,
  "lastModified": 1456320024643
}]
\end{lstlisting}
\end{minipage}
\end{custommargins}

\par
The second request (Listing~\ref{DBREQUEST}) performs the simplest API call which involves getting
all currently stored projects from the MongoDB instance. This request does not yield any extra
computation in the back-end, apart from converting the MongoDB format to the API's JSON result
format.

\newpage
\begin{custommargins}{0cm}{-2cm}
\begin{minipage}{\linewidth-1cm}
\begin{lstlisting}[label=STATICREQUEST,caption=Result of static text requests]
wrk -t100 -c100 -d10s http://perius:8000/static

@@

Response data:
Static test data for WRK not involving MongoDB 
or filesystem access. 
Lorem ipsum dolor sit amet, consectetur adipiscing elit.
\end{lstlisting}
\end{minipage}
\end{custommargins}

\par
As the second request (Listing~\ref{DBREQUEST}) involves the server answering with some payload that
is generated from the persistent storage, the third request (Listing~\ref{STATICREQUEST}) is simply
the same amount of static payload as the second request but without involving any connections to
MongoDB. This was done to be able to estimate what impact the round trip time to MongoDB and the
conversions to the response format had on the throughput.

@@

The result in Listing~\ref{TREEREQUEST} shows an average of 40 requests/s, which means this is the
real bottleneck in the application. There are two solutions to fix this bottleneck, as the project
tree will not be modified nearly as often as it is requested, the first solution would be to cache
the results of the tree requests and invalidate those caches when the tree is modified. The second
solution would be to make a more computationally feasible way of building and fetching the whole
tree from the database. This is left to implement if the need comes for it in the future. Even
though this massive bottleneck is present, it will not be a problem in a small scale production
environment as the tree is fetched approximately once every 30 seconds by active users, which means
that the application still could support at least 1200 very active users.

@@

\subsubsection{Load Testing}
Section~\ref{sec:load_testing}, specifically Listing~\ref{OKREQUEST}, shows that the HTTP server can
answer about 100K requests/s when not involving any payload other than status code 200 (OK). When
comparing that to the request which involved the server responding with a small (100 Byte) payload
(Listing~\ref{STATICREQUEST}) one can see that it is about 10\% slower to send some more data,
\textasciitilde90K requests/s. However when comparing that to the requests that needed database
access it is obvious that the HTTP server can handle all the load that it needs to, as
Listing~\ref{DBREQUEST} shows that to fetch all documents in a collection (in this case only one) is
dramatically slower, the throughput was only \textasciitilde7000 requests/s.

\par From the load testing a bottleneck of the application was found, namely building the project
trees. Three solutions for this was presented and two were tested. The first was to cache the
results of computationally heavy requests. The second was to simply make the operations more
computationally efficient, which was not tried. The third presented solution was to add indices to
keys that were often queried in MongoDB. The third solution yielded the best results and made Perius
being able to serve 2100 requests/s, which involved building the project tree. A combination of
solution one and three could possibly make Perius able to serve even more requests per second.
